### 2012-10-10 docs/architecture/architecture.tex
more updates

Different \maestro\ problems are defined in sub-directories under {\tt
  MAESTRO/SCIENCE}, {\tt MAESTRO/TEST\_PROBLEMS}, or {\tt
  MAESTRO/UNIT\_TESTS}.  To add a problem, start by creating a new
sub-directory---this is where you will compile your problem and store
all the problem-specific files.

@@

The next line defines where the top of the \maestro\ source tree is located.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  MAESTRO_TOP_DIR := ../..
\end{lstlisting}

>>>>

Different \maestro\ problems are defined in sub-directories under {\tt
  Exec/} in {\tt SCIENCE}, {\tt TEST\_PROBLEMS}, or {\tt UNIT\_TESTS}.
To add a problem, start by creating a new sub-directory---this is
where you will compile your problem and store all the problem-specific
files.

@@

The next line defines where the top of the \maestro\ source tree is located.
\begin{lstlisting}[language={[gnu]make},mathescape=false]
  MAESTRO_TOP_DIR := ../../..
\end{lstlisting}
